### 2015-11-08 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
cites for programms

%\textsl{}%!TEX TS-options = --shell-escape
%!TEX TS-program = pdflatex
\documentclass[%
   10pt,              % Schriftgroesse
   nenglish,           % wird an andere Pakete weitergereicht
   a4paper,           % Seitengroesse
   DIV11,             % Textbereichsgroesse (siehe Koma Skript Dokumentation !)
]{scrartcl}%     Klassen: scrartcl, scrreprt, scrbook, article
% -------------------------------------------------------------------------

@@

\noindent Clustal$\Omega$ is the newest extension for the Clustal family. One problem of ClustalW 

@@

better alignments than previous versions. MAFFT offers several modes. The L-INS-i mode is 

@@

FFT-NS-2 mode for this assignment. The third program MUSCLE is a iterative approach to multiple 

>>>>

bb%\textsl{}%!TEX TS-options = --shell-escape
%!TEX TS-program = pdflatex
\documentclass[%
   10pt,              % Schriftgroesse
   nenglish,           % wird an andere Pakete weitergereicht
   a4paper,           % Seitengroesse
   DIV11,             % Textbereichsgroesse (siehe Koma Skript Dokumentation !)
]{scrartcl}%     Klassen: scrartcl, scrreprt, scrbook, article
% -------------------------------------------------------------------------

@@

\noindent Clustal$\Omega$ \cite{Sievers539} is the newest extension for the Clustal family. One problem of ClustalW 

@@

better alignments than previous versions. MAFFT\cite{Katoh1} offers several modes. The L-INS-i mode is 

@@

FFT-NS-2 mode for this assignment. The third program MUSCLE \cite{Edgar1} his a iterative approach to multiple 
